\section{\nsf support requested}

% We estimate at $\sim \$2500$ per person as the cost of this event for
% the 30 participants expected at the \sympe. 
The overall budget for the \symp include all expenses for the
participants to come to the event from the United States. No
registration is being charged. We do so with the belief that to get
the most out of the participants, who have substantial expertise and
in most cases at the peak of their careers, covering these modest
expenses will be in the interests of what results we want to achieve
with this event. In addition, in the light of the pandemic and its
resultant isolation, we believe having this event in-person will make
the effort worthwhile.  We are therefore requesting \nsfe's support
for the \symp for US national travel and room and board as also
additional costs related to convening this event, as shown in Table
\ref{tab:nsf-budget}.

\begin{table}[!h]
  \footnotesize{
    \centering    
    \begin{tabular}{|p{3.0cm}|p{1.6cm}|p{10cm}|}
      \hline 
      \rowcolor{Gray}
      \bfseries Item& \bfseries Estimated Costs (US \$)&\bfseries Description\\
      \hline
      Travel & \$18,000 & \$1500 per participant travel from US home institution \\
      \hline
      Lodging& \$9000 & \$150 per night per participant X 12 X 5 nights on Angra do Heroismo, Terceira Island\\
      \hline
      Conference room rental &\$1,250 & \$250 per day rental charges X
                                        5 days\\
      \hline
      Conference Services& \$600 &  \$150 per day rental charges X 4
                                   days for A/V services and
                                   polycom for potential remote
                                   participation\\
      \hline
      Miscellany& \$100 & Miscellany for posters and writing material,
                          nametags, markers\\
      \hline
      \textbf{Total}& \$28,950&\\
      \hline        
  \end{tabular}
  \caption{Estimated budget request from \nsf for support for 12 US
    nationals at \sympe.}
  \label{tab:nsf-budget}
}
\end{table}

\paragraph{Budget justification} Our request is primarily to support
US nationals participation to/from their home institutions and their
lodging at the venue hotel in Terceira Island, Azores. Other related
items for which support is being requested are conference room rental
where the event will take place, and some ancillary expenses related
to audio/visual equipment, including a VideoConference system
(e.g. PolyCom). The latter is primarily for brief programmatic talks
from program managers/administrators in the US who might not be
willing to travel for such a brief interaction. Finally, some
miscellaneous expenses related to carrying out the poster session and
nametags. \nsf funds will not be used for any other expenses.

\subsection{Current \& Pending from other US govt. sources}

NOAA is expecting to support the \sympe. They are being requested
\$20,000. 

\subsection{Other Resources}

\fla (the Luso-American Development Foundation, Portugal) is
interested in providing support for the 3 ESR's to the symposium.
